---
title: "1st problem set: Exercise 2.1"
format: pdf
editor: visual
---



## Empirical example


**Two outcome variables:** total output and total profit from self-employment activities in the past 12 months.
As covariates use baseline household characteristics such as number of members, number of adults, head age, indicators for households doing animal husbandry, doing other non-agricultural activity, having an outstanding loan over the past 12 months, household spouse responded to the survey, another household member (excluding the household head) responded to the survey, and 81 village pair fixed effects.


```{r}
setwd("/Users/agustinff/Desktop/cemfi/2on_year/micrometrics/psets/pset2/practice")

dir_data <- "dataset_folder/data_code/Input/"

```



```{r}
#| echo: false

library(haven)

# Household survey data
# Baseline household survey 
Microcredit_BL_mini_anonym <- read_dta(  paste0(dir_data,"Microcredit_BL_mini_anonym.dta") )
View(Microcredit_BL_mini_anonym)
dim(Microcredit_BL_mini_anonym)

# Endline household survey
Microcredit_EL_mini_anonym <- read_dta(  paste0(dir_data,"Microcredit_EL_mini_anonym.dta") )
View(Microcredit_EL_mini_anonym)
dim(Microcredit_EL_mini_anonym) 

# Mini Survey data: baseline household survey data
# Short survey instrument including the key variables predicting a higher likelihood to borrow?
Microcredit_MS_anonym <- read_dta(  paste0(dir_data,"Microcredit_MS_anonym.dta") )
View(Microcredit_MS_anonym)
dim(Microcredit_MS_anonym)

names(Microcredit_EL_mini_anonym)

```


```{r}

names(Microcredit_BL_mini_anonym)


```








